Amortization of Sub-programs in Simulators

### 2019-08-31 paper/learning/notes.tex

\small\begin{table}[]
  \begin{tabular}{|l|l|l|l|}
  \hline
  \textbf{Code} & \textbf{Base} & \textbf{Timed} & \textbf{Stochastic Control Flow} \\ \hline
  \begin{cpp}
  double Splitter_Base::SelectZ(const double & delta,
  const bool & lead)
   {double zmin(0.5*(1.-sqrt(1.-delta))),
   zmax(0.5*(1.+sqrt(1.-delta))), z;
    do {
      z = zmin+ran->Get()*sqrt(1.-delta);
        } 
    while (1.-2.*z*(1.-z) < ran->Get());
  return z;
   }
  \end{cpp}&Yes&No&Yes\\ 
  \hline
  \begin{cpp}
double Decay_Channel::GenerateMass(const double& max,
const double& width) const
{
 double mass=-1.0;
 double decaymin = MinimalMass();
 if(decaymin>max) mass=-1.0;
 else if (decaymin==0.0) {
   mass=m_flavours[0].RelBWMass(decaymin, max,
                p_ms->Mass(m_flavours[0]), width);
      }
 else {
   double s=sqr(p_ms->Mass(GetDecaying()));
   double mb(0.0), mc(0.0);
   for (int i=0; i<NOut(); ++i) {
     mc+=p_ms->Mass(GetDecayProduct(i));
     if(p_ms->Mass(GetDecayProduct(i))>mb)
       mb=p_ms->Mass(GetDecayProduct(i));
   }
   mc-=mb;
   double b=sqr(mb);
   double c=sqr(mc);
   double spmax=2.0*b+2.0*c+sqrt(sqr(b)+14.0*b*c+sqr(c));
   double wmax=MassWeight(s,spmax,b,c);
   double w=0.0;
   int trials(0);
   do {
     mass=m_flavours[0].RelBWMass(decaymin, max,
                                  p_ms->Mass(m_flavours[0]), width);
     double sp=sqr(mass);
     w=MassWeight(s,sp,b,c);
     ++trials;
   } while (w<ran->Get()*wmax && trials<1000);
 }
 return mass;
}
\end{cpp}
        &  No             & Yes                     & No  \\ \hline
                &               &                     &                                  \\ \hline
  \end{tabular}
  \end{table}
\section{The unconditional acceptance probability}

>>>>

\small\begin{table}[]
  \begin{tabular}{|l|l|l|l|}
  \hline
  \textbf{Code} & \textbf{Base} & \textbf{Timed} & \textbf{Stochastic Control Flow} \\ \hline
  \begin{cpp}
  double Splitter_Base::SelectZ(const double & delta,
  const bool & lead)
   {double zmin(0.5*(1.-sqrt(1.-delta))),
   zmax(0.5*(1.+sqrt(1.-delta))), z;
    do {
      z = zmin+ran->Get()*sqrt(1.-delta);
        } 
    while (1.-2.*z*(1.-z) < ran->Get());
  return z;
   }
  \end{cpp}&Yes&No&Yes\\ 
  \hline
  \begin{cpp}
double Decay_Channel::GenerateMass(const double& max,
const double& width) 
const
{
 double mass=-1.0;
 double decaymin = MinimalMass();
 if(decaymin>max) mass=-1.0;
 else if (decaymin==0.0) {
   mass=m_flavours[0].RelBWMass(decaymin, max,
                p_ms->Mass(m_flavours[0]), width);
      }
 else {
   double s=sqr(p_ms->Mass(GetDecaying()));
   double mb(0.0), mc(0.0);
   for (int i=0; i<NOut(); ++i) {
     mc+=p_ms->Mass(GetDecayProduct(i));
     if(p_ms->Mass(GetDecayProduct(i))>mb)
       mb=p_ms->Mass(GetDecayProduct(i));
   }
   mc-=mb;
   double b=sqr(mb);
   double c=sqr(mc);
   double spmax=2.0*b+2.0*c+\\
   sqrt(sqr(b)+14.0*b*c+sqr(c));
   double wmax=MassWeight(s,spmax,b,c);
   double w=0.0;
   int trials(0);
   do {
     mass=m_flavours[0].RelBWMass(decaymin, max,
     p_ms->Mass(m_flavours[0]), width);
     double sp=sqr(mass);
     w=MassWeight(s,sp,b,c);
     ++trials;
   } while (w<ran->Get()*wmax && trials<1000);
 }
 return mass;
}
\end{cpp}
        &  No             & Yes                     & No  \\ \hline
                &               &                     &                                  \\ \hline
  \end{tabular}
  \end{table}
\section{The unconditional acceptance probability}
